\section{23/02/2024}

\subsection{From solutions to skew braces}

    \begin{definition}
        Let $(X,r)$ be a solution. The \emph{structure group} of $(X,r)$ is the group
        \begin{align*}
            G(X,r)=\langle X : xy=\lambda_x(y)\rho_y(x) \text{ for all }x,y\in X \rangle.
        \end{align*}
        The \emph{derived structure group} of $(X,r)$ is the group
        \begin{align*} 
            A(X,r)=\langle X : x\lambda_x(y)=\lambda_x(y)\lambda_{\lambda_x(y)}\rho_y(x) \text{ for all }x,y\in X \rangle.
        \end{align*}
    \end{definition}

        
    \begin{theorem}[\cite{MR1722951} or \cite{LYZ00}]\label{thm:structuregroup}
    Let $(X,r)$ be a solution.
    Then, there exists a unique structure of skew brace with multiplicative group the structure group isomorphic to $G(X,r)$, additive strucutre isomorphic to $A(X,r)$ and such that $\lambda_{i(x)}(i(y))=i(\lambda_x(y))$ for all $x,y\in X$, where $\iota: X\to G(X,r), x\mapsto x$ is the canoical map. 
    \end{theorem}

    \begin{proof}
        Omitted.
    \end{proof}

    Note that the map $i$ in the previous theorem is not necessarily injective.

    \begin{example}
        Let $X=\{1,2,3,4\}$, $\lambda= (1\ 2)$ and $\rho=(3\ 4)$. Since $\lambda\rho=\rho\lambda$, we have that $r:X\times X\to X \times X$ defined by $r(x,y)=(\lambda(y),\rho(x))$ gives a solution. In $G(X,r)$ the elements $1$ and $2$ are identified and also $3$ and $4$. Indded in $G(X,r)$ we have 
        \begin{align*}
            1\circ 1 = \lambda(1)\circ \rho(1) = 2 \circ 1 \implies 1 = 2,\\
            3\circ 3 = \lambda(3)\circ \rho(3) = 3 \circ 4 \implies 3=4.
        \end{align*}
        Therefore, $i$ is not injective. 
    \end{example}

    The structure skew brace defined in the previous theorem satisfies the following universal property.
    
    \begin{proposition}
        Let $(B,+,\circ)$ be a skew brace, $j\colon X\rightarrow B$ be a map such that $\lambda_{j(x)}(j(y))=j(\lambda_x(y))$ and $j(x)\circ j(y)=j(\lambda_x(y))\circ j(\rho_y(x))$, for all $x,y\in X$. Then there exists a unique homomorphism of skew braces $f\colon G(X,r)\rightarrow B$ such that $fi=j$, i.e.
        \begin{equation*}
        \begin{tikzcd}
            X \arrow[r,"j"] \arrow[d,swap,"i"] &
            B \arrow[dl,swap, dashed,"f"] 
            \\
            G(X,r) 
        \end{tikzcd}
        \end{equation*}
    \end{proposition}

    \begin{proof}
        Omitted.
    \end{proof}

    \subsection{The permutation group of a solution}

    If $(X,r)$ is a finite solution we can consider a finite quotient (as skew brace) of the strucure group that governs important property of such solution. 

    Let $(X,r)$ be a solution. Consider the structure group $G(X,r)$ of the solution $(X,r)$. Let $i\colon X\to G(X,r)$ be the natural map. 

    \index{Solution!permutation group}
    The \emph{permutation group} of $(X,r)$ is the subgroup
\[\mathcal{G}(X,r)=\langle (\lambda_x,\rho^{-1}_x) : x\in X\rangle\subseteq\Sym_X\times\Sym_X.\]
Since 
\[ \lambda_x\lambda_y=\lambda_{\lambda_x(y)}\lambda_{\rho_y(x)}\quad\text{and}\quad \rho^{-1}_x\rho^{-1}_y=\rho^{-1}_{\lambda_x(y)}\rho^{-1}_{\rho_y(x)} \]
for all $x,y\in X$, there exists a unique group homomorphism
$h\colon G(X,r)\to \mathcal{G}(x,r)$ such that $hi(x)=(\lambda_x,\rho^{-1}_x)$ for all $x\in X$. We write $h(a)=(\lambda_a,\rho_a^{-1})$,
for all $a\in G(X,r)$.
By Theorem~\ref{thm:structuregroup}, $G(X,r)$ has a unique structure of skew brace with multiplicative group the structure group $G(X,r)$ and $\lambda_{i(x)}(i(y))=i(\lambda_x(y))$ for all $x,y\in X$. One can prove that $\ker h$ is an ideal of the skew brace $G(X,r)$. Hence, $\mathcal{G}(X,r)$ inherits a skew brace structure form $G(X,r)$.

Given a skew brace $(A,+,\circ)$ with $(A,+)$ abelian, Bachiller, Cedó and Jespers in \cite{} provided a method to recostruct all (involutive) solutions such that $\mathcal{G}(X,r)$ is isomorphic as skew brace to $A$. In \cite{}, Bchiller generalised this construction dropping the assumption $(A,+)$ abelian.

\subsection{Simple solutions}

Describing simple solution is a very hard and challenging task. A strategy to tackle such problem is to focus on ``building blocks'', such us indecomposable solutions and simple solutions. 

\begin{definition}
    A solution $(X,r)$ is said to be \emph{decomposable} if there exist $\emptyset \neq Y,Z \subseteq X$ such that $Y\cup Z = X$, $Y \cap Z = \emptyset$ and $r(Y\times Y)\subseteq Y\times Y$, $r(Z\times Z)\subseteq Z \times Z$. Otherwise, $(X,r)$ is said \emph{indecomposable}.
\end{definition}

It is not difficult to prove that a solution $(X,r)$ is indecomposable if the group $\langle \lambda_x, \rho_y \colon x, y \in \rangle$ acts transitivelly on $X$.

\begin{definition}
    A solution $(X,r)$ is said to be \emph{simple} if for any epimorphism of solutions $\varphi: (X,r) \to (Y,t)$, we have either $\varphi$ an isomorphis or $Y$ as singleton.
\end{definition}

One can prove that a simple solution is in particular indecomposable. 

Cedó and Okniński in \cite{} proved that ome simple skew brace with additive structure abelian provide examples of (involutive) simple solutions. 

Joyce in 1982 studied simple racks and provided an algebraic characterisation of such racks. By Proposition~\ref{prop:rack}, a rack provide a solution and it is not difficult to see that simple racks are in particular examples of simple solutions. 

In join work with Jespers, Kubat and Van Antwerpen \cite{}, we obtain a brace theoretic classification of simple solutions. 

\begin{theorem}
    A simple solution $(X,r)$ is one of the following type:
    \begin{enumerate}
        \item $(X,r)$ is a simple permutation solution,
        \item $(X,r)$ is a simple square-free\footnote{A solution $(X,r)$ is square-free if $r(x,x)=(x,x)$ for every $x\in X$.} derived solution (i.e. it is a simple quandle\footnote{A rack $(X,\triangleleft)$ is a quandle if $x\triangleleft x = x$, for every $x\in X$.}),
        \item $(X,r)$ is a simple solution embedded in a solution associated to a finite skew brace. 
    \end{enumerate}
\end{theorem}

\subsubsection{Simple permutation solution}

Recall that a $(X,r)$ is a permutation solution if there exist $\lambda,\rho$ commuting permutations such that $r(x,y)=(\lambda(y),\rho(x))$.

We can give a combinatorial characterisation of simple permutation solutions.

\begin{proposition}
    A permutation solution $(X,r)$ is simple if and only if the caridnality of $X$ is a prime number $p$, the group $H=\langle\lambda,\rho\rangle$ is cyclic of order $p$.

    In particular, $(X,r)$ solution is isomorphic to $(\mathbb{Z}_p,t)$ such that $t(x,y)= (y+a,x+b)$ with $,a,b\in \mathbb{Z}$ and$(a,b)\neq (0,0)$.
\end{proposition}

\subsubsection{Simple quandle}

The description of simple square-free derived solutions coiced with the description obtained by Joyce of simple quandles. 

\begin{proposition}
    A square-free derived solution $(X,r)$ is simple if and only if $(X,r)$ embedd in a solution $(A,r)$ where $A$ is a finite group and $r(y, y^{-1}xy)$ such that
    \begin{itemize}
        \item $X$ is a conjucacy class genereting $A$,
        \item the derived subgroup $[A,A]$ is the smallest non-zero normal subgroup of $A$,
        \item the quotient group $A/[A,A]$ is a cyclic group,
        \item the center $Z(A)$ is trivial.
    \end{itemize}
\end{proposition}

\subsubsection{Simple solutions embedded in solutions associated to finite skew braces}

Let $(A,+,\circ)$ be a skew brace. In analogy with radical rings, we can associate to $A$ another binary operation $\ast:A\times A\to A$ such that $a\ast b = -a+a\circ b +b$, for every $a,b\in A$.

\begin{exercise}\label{ex:A2}
    Let $(A,+,\circ)$ be a skew brace. Define $A^2$ the additive subgroup generated by $\{a\ast b=-a+a\circ b - b \colon a,b\in A\}$. Prove that 
    $A^2$ is an ideal of $A$.
\end{exercise}

The ideal $A^2$ plays for skew braces a simplar role that the derived subgroup plays for groups. With this observation in mind, it might be not surpising the following proposition. 

\begin{proposition}
    A square-free solution $(X,r)$ which is not a derived solution nor a permutation solution is simple if and only if $(X,r)$ embedd in a solution asoociated to a non-trivial skew brace $(A,r_A)$ such that
    \begin{itemize}
        \item $X$ generates additively $A$,
        \item the ideal $A^2$ is the smallest non-zero ideal of $A$,
        \item the quotient skew brace $A/A^2$ is trivial skew brace with additive (and multiplicative) group cyclic,
        \item the action of $A^2$ on $X$ is transitive.
    \end{itemize}
\end{proposition}

Let us explain what the last item means. Let $A$ be a skew brace, $X\subset A$ and $I$ an ideal of $A$. We say that $I$ \emph{acts} on $X$ if $X$ is invariant uder the action of the group $(I,+)\rtimes (I,\circ)$ (where the semidirect product is given by the $\lambda$-map).